Jackknife

### 2021-02-14 analysis/rev_prototyping/jackknife.Rmd
fixese

  # ind_pool_mat <- as.matrix(dplyr::select(site_df, rank, abund))
  # 
  # ind_pool <- unlist(apply(ind_pool_mat, MARGIN = 1, FUN = make_ind_pool_species))
  # 
  # sampled_ind <- replicate(n = nsims, expr = sample_ind_pool(ind_pool, nind_to_sample), simplify = F)
  # 
  sampled_ind <- rmultinom(n = nsims, size = nind_to_sample, prob = site_df$abund)

  sampled_ind_df <- as.data.frame(sampled_ind) %>%
    dplyr::mutate(species = dplyr::row_number()) %>%
    tidyr::pivot_longer(-species, names_to = "sim", values_to = "abund") %>%
    filter(abund > 0) %>%
    dplyr::group_by(sim) %>%
    dplyr::arrange(abund) %>%
    dplyr::mutate(rank = dplyr::row_number()) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(sim, rank) %>%
    dplyr::mutate(sim = substr(sim, 2, nchar(sim))) %>%
    dplyr::select(-species)

>>>>

  ind_pool_mat <- as.matrix(dplyr::select(site_df, rank, abund))

  ind_pool <- unlist(apply(ind_pool_mat, MARGIN = 1, FUN = make_ind_pool_species))

  sampled_ind <- replicate(n = nsims, expr = sample_ind_pool(ind_pool, nind_to_sample), simplify = F)

  sampled_ind = unique(sampled_ind)

# 
#   sampled_ind <- rmultinom(n = nsims, size = nind_to_sample, prob = site_df$abund)

  sampled_ind_df <- dplyr::bind_rows(sampled_ind, .id = "sim") %>%
    dplyr::group_by(sim, species) %>%
    dplyr::summarize(abund = dplyr::n()) %>%
    dplyr::ungroup() %>%
    dplyr::filter(abund > 0) %>%
    dplyr::select(-species) %>%
    dplyr::group_by(sim) %>%
    dplyr::arrange(abund) %>%
    dplyr::mutate(rank = dplyr::row_number()) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(sim, rank)
